---
title: "Regional Academy Testing - August"
author: "Ciaran Miller"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "cmiller@wru.wales"
output:
  epuRate::epurate:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---


<br><br>

> This website is designed to show an overview of the data collected during Regional Academy testing. If you feel something is missing let me know, and I can do my best to add it.

# The basics
***
It's generally good to start really broad when looking at all of this data, and think about what are some of the really easy questions to answer. This is all the data we collected this testing block:
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(rmarkdown)    # You need this library to run this template.
library(epuRate)      # Install with devtools: install_github("holtzy/epuRate", force=TRUE)
library(janitor)
library(gt)
library(gtsummary)

data <- read_csv("data/december_data.csv") %>% 
  clean_names()

data %>% head(5)
```

So it's nicer to look at specific questions, and answer step by step.

Here's all the anthropometry measurements by position:
```{r, message=FALSE, warning=FALSE}
anthro <- data %>% 
  select(position, body_weight, height_13, fat_free_mass, percent_bf)


anthro_summary <- anthro %>%
  tbl_summary(by = "position",
              statistic = all_continuous() ~ "{mean} ±{sd}",
              label = list("body_weight" ~ "Body Weight",
                           "height_13" ~ "Height",
                           "fat_free_mass" ~ "Fat-Free Mass",
                           "percent_bf" ~ "BF %")
  ) %>%
  as_gt() %>%
  tab_spanner(label = "Position",
              columns = 6:14)
  
anthro_summary
```


And a similar look at force & power metrics:
```{r, message=FALSE, warning=FALSE}
force_power <- data %>%
  select(position, peak_power, w_kg, isosqt_peak_force, pf_bm) %>%
  drop_na()

force_power_summary <- force_power %>%
  tbl_summary(by = "position",
              statistic = all_continuous() ~ "{mean} ±{sd}",
              label = list("peak_power" ~ "CMJ Peak Power",
                           "w_kg" ~ "Relative Power",
                           "isosqt_peak_force" ~ "ISO Peak Force",
                           "pf_bm" ~ "Relative Peak Force"))

force_power_summary
```



